Age-related changes in plant growth and traits

### 2015-05-19 results_RAschedules_shorter.Rmd
created separate "RA_schedules_shorter" results file.

source("scripts/summary_dataframes.R")
plot_yvar_vs_xvar <- function(data, yvar = "y", xvar = "x", ...) {
  Y <- data[[yvar]]
  X <- data[[xvar]]
  plot(Y ~ X, data=data,  cex.axis=.8, las=1, pch=16, ...)
}

plot_yvar2_vs_xvar2 <- function(data, yvar2 = "y", xvar2 = "x", ...) {
  Y <- data[[yvar2]]
  X <- data[[xvar2]]
  plot(Y ~ X, data=data,  cex.axis=.8, las=1, pch=16, ...)
}

summarise_fit <- function(x) {
  data.frame(
    select(glance(x), r.squared, p.value),
    n= length(resid(x)),
    a = coef(x)[1],
    b = coef(x)[2]
  )
}

summarise_all_fits <- function(x) {
  tmp <- lapply(x, summarise_fit) %>%
    bind_rows
  data.frame(species=names(x), tmp)
}

summarise_fit_2var <- function(x) {
  data.frame(
    select(glance(x), r.squared, p.value),
    n= length(resid(x)),
    intercept = coef(x)[1],
    coef_var1 = coef(x)[2],
    coef_var2 = coef(x)[3],
    coef_var1var2 = coef(x)[4],
    SS_var1 = anova(x)[1,2],
    SS_var2 = anova(x)[2,2],
    SS_var1var2 =anova(x)[3,2]
      )
}

summarise_all_fits_2var <- function(x) {
  tmp <- lapply(x, summarise_fit_2var) %>%
    bind_rows
  data.frame(species=names(x), tmp)
}

xy.error.bars <- function (x,y,xbar,ybar) {
  plot(x,y,pch=16, ylim=c(min(y-ybar),max(y+ybar)),xlim=c(min(x-xbar),max(x+xbar)))
  arrows(x,y-ybar,x,y+ybar,code=3,angle=90, length=0.1)
  arrows(x-xbar,y,x+xbar,y,code=3,angle=90, length=0.1)
}

se_function <- function(mean1,se1) {
for(i in 1:14) {
arrows(i,mean1[i]+se1[i],i,mean1[i]-se1[i],code=3,angle=90, length=0.1)
}
}

words.top.right.logxy <- function (x) {
output <- data.frame(select(glance(x), r.squared, p.value))
output <- round(output,4)
text(10^((0.75*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),10^((0.93*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),paste("r squared = ",output[1]),adj=0,cex=.9)
text(10^((0.75*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),10^((0.88*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),paste("p-value = ",output[2]),adj=0,cex=.9)
text(10^((0.99*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),10^((0.98*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),summary(mod)[1],cex=.7,adj=1)
}

words.top.right.logx <- function (x) {
output <- data.frame(select(glance(x), r.squared, p.value))
output <- round(output,4)
text(10^((0.75*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),((0.93*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),paste("r squared = ",output[1]),adj=0,cex=.9)
text(10^((0.75*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),((0.88*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),paste("p-value = ",output[2]),adj=0,cex=.9)
text(10^((0.99*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),((0.98*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),summary(mod)[1],cex=.7,adj=1)
}

words.top.right <- function (x) {
output <- data.frame(select(glance(x), r.squared, p.value))
output <- round(output,4)
text(((0.75*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),((0.93*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),paste("r squared = ",output[1]),adj=0,cex=.9)
text(((0.75*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),((0.88*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),paste("p-value = ",output[2]),adj=0,cex=.9)
text(((0.99*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),((0.98*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),summary(mod)[1],cex=.7,adj=1)
}

words.bottom.right.logxy <- function (x) {
output <- data.frame(select(glance(x), r.squared, p.value))
output <- round(output,4)
text(10^((0.75*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),10^((0.12*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),paste("r squared = ",output[1]),adj=0,cex=.9)
text(10^((0.75*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),10^((0.07*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),paste("p-value = ",output[2]),adj=0,cex=.9)
text(10^((0.99*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),10^((0.02*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),summary(mod)[1],cex=.7,adj=1)
}

words.bottom.right.logx <- function (x) {
  output <- data.frame(select(glance(x), r.squared, p.value))
  output <- round(output,4)
  text(10^((0.75*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),((0.12*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),paste("r squared = ",output[1]),adj=0,cex=.9)
  text(10^((0.75*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),((0.07*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),paste("p-value = ",output[2]),adj=0,cex=.9)
  text(10^((0.99*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),((0.02*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),summary(mod)[1],cex=.7,adj=1)
}
```

#Changes in growth and tissue allocation with age and size
* Part of this paper would be to look at how different "types of" species fall out with respect to the various plots - i.e. canopy species (BAER, HATE, PELA), short-lived species (BOLE, PILI, COER), longer-lived understory species

###More ways to ask how much - and when - reproduction impacts growth  
- It is clear that different species reach a different "proportion maxH" (RSOM) before reproducing. Need to do curve fitting to determine where this occurs.  
- The plot of Growth Investment vs. PropH shows a decrease in growth rate at a given PropH (for most species). Is this the same PropH at which reproduction begins?  
- It seems that some of the early reproducers begin reproducing at a larger PropH, as predicted by others. But because they allocate so much to reproduction, their growth rate declines more precipitously with the onset of reproduction.

@@

```{r, echo=FALSE,message=FALSE, fig.width=12, fig.height=6, out.width=792, out.height=576}
yvar <- "RA"
xvar <- "PropH"

yvar2 <- "RA"
xvar2 <- "FinalWeight"

@@

}

plot.new()
```

```{r, echo=FALSE,message=FALSE, fig.width=12, fig.height=6, out.width=792, out.height=576}
yvar <- "ReproInv"
xvar <- "PropH"

@@

@@

for(spp in names(data)) {
  par(mfrow=c(1,2), cex=1, omi=c(.1,0.3,.5,0.2), mai=c(1.2,1,.5,0.2))  
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar, 
                    main=spp, ,log="y", xlab=xvar, ylab=yvar)
  plot_yvar2_vs_xvar2(data[[spp]], yvar2, xvar2, 
                    main=spp, log="xy", xlab=xvar2, ylab="")

}

par(mfrow=c(1,1), pin=c(5,7),mar=c(5,4,4,2)+.1,omi=c(.1,.1,.1,.1))
```

```{r, echo=FALSE,message=FALSE, fig.width=7, fig.height=7, out.width=792, out.height=576}
plot((ReproInv)~(PropH), SummaryInd, log="y",col=col.spp[as.factor(species)],pch=16,xlim=c(4e-03,1),xlab=xvar)
legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

plot(ReproInv~FinalWeight, SummaryInd, log="xy",col=col.spp[as.factor(species)],pch=16)
legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

plot(ReproInv~height, SummaryInd, log="xy",col=col.spp[as.factor(species)],pch=16)
legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
```

* Reproductive investment vs. PropH
```{r, echo=FALSE,message=FALSE, fig.width=7, fig.height=7, out.width=792, out.height=576}
yvar <- "ReproInv"
xvar <- "PropH"

@@

##RA schedules (vs. propH)  
- RA schedules still look "best" plotted against age; not shown here  
- these curves are particularly good for a number of species such as EPMI, COER, PELA  
- they also show that for PILI that among individuals that reproduce, the "potential" RA decreases with increasing propH  
- when all data points are included, all species except PEPU, PHPH, and PULU show increasing RA with increasing height  
- when RA =0 is excluded, the following species still have a significant positive correlation: BOLE, COER, EPMI, GRBU, GRSP, HATE. LEES and PELA have a p-value between 0.05-0.10   
- PEPU has a negative correlation - matches Mark's suggestion that it is "hanging on"  
- There are species - such as BOLE - which have a much "cleaner" plot against age instead of PropH (or any other size measure). This indicates that these species are programmed to reproduce at a certain "rate" regardless of their size

```{r, echo=FALSE, message=FALSE}
plot((RA~PropH), SummaryInd, col=col.spp[as.factor(species)],pch=16)
legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

plot(RA~PropH, SummaryInd, col=col.age[as.factor(age)],pch=16)
legend("topleft",legend=names(labels.age),col=col.age,pch=16, cex=.8,bty="n")

yvar <- "RA"
xvar <- "PropH"

data <- subset(SummaryInd)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(asin(sqrt(x[[yvar]])) ~  (x[[xvar]])))
results <- summarise_all_fits(lmfits)

@@

```{r, echo=FALSE,message=FALSE}
plot((1+ReproInv)~GrowthInv, SummaryInd, log="xy", col=col.spp[as.factor(species)],pch=16)
legend("bottomright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
```

@@

```{r, echo=FALSE,message=FALSE}
plot(RA~RGR, SummaryInd, log="xy", col=col.spp[as.factor(species)],pch=16)
legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

mod <- lm(RGR~asin(sqrt(RA))*species,SummaryInd)
anova(mod)
```

@@

###Looking jointly at effects of RA and PropH on growth inveestment
- Model analyzed is: lm(log([[GrowthInv]]) ~  asin(sqrt([[RA]]))*asin(sqrt([[PropH]]))))  
- The canopy species have, not suprisingly, a very obvious maxH, with Growth Investment or RGR tapering markedly at the maxH is approached. In these species growth investment is poorly correlated with RA, but well correlated with height.  
- In some of the mid-height species (GRSP, BOLE, GRBU), growth investment is very poorly correlated with height, but better correlated with RA - in other words, increased RA = less growth.  
- One of the difficult features interpreting this, is that there are species with overall higher correlations and overall lower correlations, and this pattern dominates, not the relative strength  
- My current analyses still lack the ability to tease apart the most obvious pattern - because I don't actually want to show that growth and height are correlated, so much as that the   asymptoting of growth is correlated with height - i.e. the change in slope of the relationship.  
```{r, echo=FALSE, message=FALSE}
yvar <- "GrowthInv"
xvar <- "RA"
x2var <- "PropH"

@@

#Shifts in accessory costs across species and ages
##Overall results
- Accessory costs higher for bigger seeds

- Accessory costs higher for bigger species; these are the same species that invest less in RA

- Of course there is also a correlation between seed size and plant size, but actually not as strong as the accessory cost one, presumably because older plants have lower accessory costs as well as species that are inherently bigger

- A number of species show fairly consistent declines in accessory costs with various measures of "bigger", including size, age, RA. Other species show no patterns  
- Lower pre-pollination costs in plants with higher RA: 9 (of 14) species decrease the proportion of reproductive investment in "pre-pollination" tissues as their RA increases. in other words, they get better returns on investment the more they invest. (This is just a pattern within, not across, species)  
- Species very different in which accessory tissues they invest the most in - which reflects the differences in basic structure (i.e. Banksia cones), but also more subtlely that some species abort lots of buds (pre-pollination aborted), while other species abort more fully formed flowers  
- Haven't actually run all the tests, but assume all reproductive tissue types will differ in proportional allocation across species
- For most of the statistical analyses, the youngest site has been removed, since it included individuals that were harvested while flowering (and therefore never "got to" set fruit) and automatically have no "successful" reproduction. There are of course some individuals like this at other ages as well, but far fewer

##Basic questions
###How do accessory costs shift with seed size?
- Larger-seeded species have higher accessory costs. 
- Also shown in other studies and suggested as a mechanism for why angiosperms were able to have such small seeds (relative to gymnosperms, with no decrease in proportional accessory costs - with decreasing size)  
-  As shown below, bigger species also have higher accessory costs (and also bigger seeds - cause vs. effect unknown)
```{r, echo=FALSE,message=FALSE}
mod <- lm(log(seed_size)~asin(sqrt(PerAcc_mean)),SummarySpp)
plot(PerAcc_mean~seed_size,SummarySpp, log="xy", pch=16,col=col.spp[as.factor(species)])
legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
words.bottom.right.logxy(mod)
```

###Why measure "Total Reproductive Investment" instead of "seed weight" or "fruit weight"?  
- The R^2 for the plot of total reproductive investment against total plant size is much stronger than plotting seed weight against total plant size (R^2 = 0.61 vs 0.33)  
- Adding propagule + packaging & dispersal (i.e. successful reproduction costs), improves the fit somewhat (R^2 =0.55)  
- Total pre-pollination costs are also well-correlated with plant size, indicating bigger plants have more flowers
- NEXT: Once I have all parts weights, plot against fruit weight

```{r, echo=FALSE,message=FALSE}
mod <- lm (log(FinalWeight)~log(ReproInv), data=subset(SummaryInd,ReproInv>0))
plot(ReproInv~FinalWeight,data=subset(SummaryInd,ReproInv>0), log="xy",col=col.spp[as.factor(species)], pch=16)
legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
words.bottom.right.logxy(mod)

mod <- lm (log(FinalWeight)~log(Prop), data=subset(SummaryInd,Prop>0))
plot(Prop~FinalWeight,data=subset(SummaryInd,Prop>0), log="xy",col=col.spp[as.factor(species)], pch=16)
legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
words.bottom.right.logxy(mod)

mod <- lm (log(FinalWeight)~log(Prop+PD), data=subset(SummaryInd,Prop>0))
plot((Prop+PD)~FinalWeight,data=subset(SummaryInd,Prop>0), log="xy",col=col.spp[as.factor(species)], pch=16)
legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
words.bottom.right.logxy(mod)

mod <- lm (log(FinalWeight)~log(PrePol_All), data=subset(SummaryInd,PrePol_All>0))
plot((PrePol_All)~FinalWeight,data=subset(SummaryInd,PrePol_All>0), log="xy",col=col.spp[as.factor(species)], pch=16)
legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
words.bottom.right.logxy(mod)
```

###Looking at counts
- Final weight vs. #flowers+buds
- Final weight vs. #fruit

##Across species patterns of note
###Size versus proportional propagule investment
- Species that are bigger (by weight) invest a lower proportion of their reproduction in propagules  
   1.  This is another way of showing that larger species get less of a return on their investment in reproduction. They have higher accessory costs. 
   - There is also an increase in propagule investment with age
```{r, echo=FALSE,message=FALSE, fig.width=14, fig.height=7, out.width=792, out.height=576}
mod <- lm(log(FinalWeight) ~ (log(PerPropagule))+age,data=subset(SummaryInd,PerPropagule>0))
summary(mod)
plot(PerPropagule ~FinalWeight, data=subset(SummaryInd,RA>0&PerPropagule>0),log="xy", col=col.spp[as.factor(species)],pch=16)
legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
words.top.right.logxy(mod)
text(10^((0.70*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),10^((0.85*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),"includes age effect",adj=0) 
```

- Species that are bigger also invest a lower proportion of their TOTAL surplus energy in propagules (proportion propagules*RA) 
  + This is noisier than looking simply at proportion reproductive allocation to propagules, because of the RA effects - see below
```{r, echo=FALSE, message=FALSE}
mod <- lm(log(FinalWeight) ~ (log(PropAllocation))*age,data=subset(SummaryInd,PerPropagule>0))
plot(PropAllocation ~FinalWeight, data=subset(SummaryInd,RA>0&PerPropagule>0),log="xy", col=col.spp[as.factor(species)],pch=16)
legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
words.top.right.logxy(mod)
text(1000,.6e-4,"includes age effect (increase in Prop Allocation with age)",adj=0)
summary(mod)
```

- Looking at RA with plant size is not very informative, because:
  1. RA increases with plant size within a species  
  2. decreases with plant size across species  
  3. in combination they are noisy
- The first plot is all points  
- The second plot is just 7-year olds, showing the decrease in RA with plant size  
```{r, echo=FALSE, message=FALSE}
mod <- lm(log(FinalWeight) ~ (log(RA)),data=subset(SummaryInd,RA>0))
plot(RA ~FinalWeight, data=subset(SummaryInd,RA>0),log="xy", col=col.spp[as.factor(species)],pch=16)
legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
words.bottom.right.logxy(mod)
anova(mod)

mod <- lm(log(FinalWeight) ~ (log(RA)),data=subset(SummaryInd,RA>5e-3&age==7))
plot(RA ~FinalWeight, data=subset(SummaryInd,RA>5e-3&age==7),log="xy", col=col.spp[as.factor(species)],pch=16)
legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
words.top.right.logxy(mod)
```

- A model including the effect of both PerPropagule and RA on FinalWeight confirms this - there is a strong species effect and strong PerPropagule effect, but RA is much less significant  
```{r, echo=FALSE, message=FALSE}
mod <- lm(log(FinalWeight) ~ (log(RA))*log(PerPropagule)*species,data=subset(SummaryInd,PerPropagule>0))
anova(mod)
```

- Proportional investment in all pre-pollination tissues is uncorrelated with plant size (at most ages)  
  +  if age included in model, becomes highly significant  
```{r, echo=FALSE, message=FALSE}
mod <- lm(log(FinalWeight) ~ asin(sqrt(PerPrePol_All)),data=subset(SummaryInd,PerPrePol_All>0&age>3))
plot(asin(sqrt(PerPrePol_All)) ~ FinalWeight, data=subset(SummaryInd,PerPrePol_All>0),log="x", col=col.spp[as.factor(species)],pch=16)
legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
words.top.right.logx(mod)
```

- Shifts in packaging and dispersal costs with plant weight
- Species very different from one another, but no shift with size 
- Also no pattern w/r RA (not shown)
```{r, echo=FALSE, message=FALSE}
mod <- lm(log(FinalWeight) ~ asin(sqrt(PerPackDisp)),data=subset(SummaryInd,PerPackDisp>0))
plot(asin(sqrt(PerPackDisp)) ~FinalWeight, data=subset(SummaryInd,PerPackDisp>0),log="x", col=col.spp[as.factor(species)],pch=16)
legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
words.top.right.logx(mod)
```

###Across species summary
- greater plant weight = lower RA  (spending more on growth and survival)**  
- greater plant weight = lower proportion to propagules  (bigger species get less for their allocation)**  
- plant weight = little effect on pre-pollination tissues

##Within species (across age, size, or RA) patterns to note
- Only COER and HATE increase allocation to propagules with increased plant size  
- This, together with other plots, indicates that only the plants (of a species) that have higher RA, have higher propagule investment; but not all bigger individuals have higher RA
NOTE: Plot nearly same as above, except y-axis arcsine transformed, not log transformed and R^2 values without species term
```{r, echo=FALSE, message=FALSE}
yvar <- "PerPropagule"
xvar <- "FinalWeight"

data <- subset(SummaryInd, Total>0)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(asin(sqrt(x[[yvar]])) ~  log(x[[xvar]])))
results <- summarise_all_fits(lmfits)

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=2)
results$b <- round(results$b,digits=2)
results

mod <- lm(log(FinalWeight)~asin(sqrt(PerPropagule)),data=subset(SummaryInd,PerPropagule>0))
plot(asin(sqrt(PerPropagule))~log(FinalWeight), data=subset(SummaryInd,PerPropagule>0),col=col.spp[as.factor(species)],pch=16)
legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
words.top.right(mod)
```

- Allocation to propagules increases with RA in all species except EPMI, PHPH, PILI, PUTU  
- again, probably a figment of overall increased allocation (higher RA) if propagules form  
```{r, echo=FALSE, message=FALSE}
yvar <- "PerPropagule"
xvar <- "RA"

data <- subset(SummaryInd, Total>0)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(asin(sqrt(x[[yvar]])) ~  asin(sqrt(x[[xvar]]))))
results <- summarise_all_fits(lmfits)

results

mod <- lm(asin(sqrt(RA))~asin(sqrt(PerPropagule)),data=subset(SummaryInd,PerPropagule>0))
plot(asin(sqrt(PerPropagule))~asin(sqrt(RA)), data=subset(SummaryInd,PerPropagule>0),col=col.spp[as.factor(species)],pch=16)
legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
words.top.right(mod)
```

###Change in proportional allocation to pre-pollination tissues with plant weight 
- only a few species show a significant correlation -> as plants grow, they don't shift this allocation  
```{r, echo=FALSE, message=FALSE}
yvar <- "PerPrePol_All"
xvar <- "FinalWeight"

data <- subset(SummaryInd, Total>0)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(asin(sqrt(x[[yvar]])) ~  log(x[[xvar]])))
results <- summarise_all_fits(lmfits)

###Change in proportional allocation to pre-pollination tissues with RA
- 9 species decrease allocation to pre-pollination tissues with increased RA  
- this could simply be because when/if flowers are pollinated, there is increased reproductive investment, increasing RA and decreasing pre-pollination allocation  
- Interesting that RA increases with plant size, and pre-pollination decreases with RA, but very low correlation between pre- pollination allocation and plant size  
```{r, echo=FALSE, message=FALSE}
yvar <- "PerPrePol_All"
xvar <- "RA"

data <- subset(SummaryInd, Total>0)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(asin(sqrt(x[[yvar]])) ~  asin(sqrt(x[[xvar]]))))
results <- summarise_all_fits(lmfits)

results

mod <- lm(asin(sqrt(RA))~asin(sqrt(PerPrePol_All)),data=subset(SummaryInd,PerPrePol_All>0))
plot(asin(sqrt(PerPrePol_All))~asin(sqrt(RA)), data=subset(SummaryInd,PerPrePol_All>0),col=col.spp[as.factor(species)],pch=16)
legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
words.top.right(mod)
```

- Quite a few species (BAER, BOLE, COER, GRBU, GRSP, HATE, HEPU, PEPU, PHPH increase the percent reproductive investment spent on packaging and dispersal with age 
- This probably reflects increased seed set with age and the simulatenous increase in this pool
```{r, echo=FALSE, message=FALSE}
yvar <- "PerPackDisp"
xvar <- "RA"

data <- subset(SummaryInd, Total>0)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(asin(sqrt(x[[yvar]])) ~  asin(sqrt(x[[xvar]]))))
results <- summarise_all_fits(lmfits)

###Within species summary
- greater plant weight = higher RA  (plants allocate more to reproduction when bigger/older)**
- plant weight = little effect on proportion to propagules  
- plant weight = little effect on pre-pollination tissues  
- higher RA = lower allocation to pre-pollination tissues (probably because more seed set)
- higher RA = greater allocation to propagules (probably because more seed set)

##Shifts in proportion to tissue types across species  
- Propagule allocation across species  
- COER, EPMI, LEES, PILI invest the most energy in propagules  
- HATE invests by far the least into propagules  
```{r, echo=FALSE, message=FALSE}
#mod <- lm(asin(sqrt(PerPropagule)) ~ species-1, data=subset((SummaryInd,Total>0))
#tmp <- summary(mod)
#tmp <- tmp$coefficients
#tmp <-as.data.frame(tmp)
#tmp <- cbind(names(labels.spp),tmp)
#names(tmp) <- c("species","estimate.trans","se.trans","t.value","p.value")
mean1 <- SummarySpp$PerPropagule_mean
se1 <- SummarySpp$PerPropagule_se
plot(mean1~species,SummarySpp,cex.axis=.7,pch=16,log="y",ylim=c(.002,.25),main="Percent reproductive investment put into propagules")
se_function(mean1,se1)
```

- pre-pollination allocation across species

```{r, echo=FALSE, message=FALSE}
mean1 <- SummarySpp$PerPrePol_All_mean
se1 <- SummarySpp$PerPrePol_All_se
plot(mean1~species,data=subset(SummarySpp),cex.axis=.8,pch=16,ylim=c(.1,1),main="Percent reproductive investment put into pre-pollination tissues")
se_function(mean1,se1)
```

- just looking among plants >3 years old

```{r, echo=FALSE, message=FALSE}
tmp <- SummaryInd %>%
  filter(Total!=0&age>3) %>%
  group_by(species) %>%
  summarise_each(funs(mean, se), PerPrePol_All)

>>>>

source("scripts/summary_dataframes.R")
source("scripts/functions.R")
```

@@

###Plots of size against reproductive investment
* Plots of total reproductive investment against size or height are both highly significant
```{r, echo=FALSE,message=FALSE, fig.width=7, fig.height=7}
mod <- lm(log(FinalWeight)~log(ReproInv), data=subset(SummaryInd,ReproInv>0))
plot(ReproInv~FinalWeight, SummaryInd, log="xy",col=col.spp[as.factor(species)],pch=16)
legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
words.bottom.right.logxy(mod)

mod <- lm(log(height)~log(ReproInv), data=subset(SummaryInd,ReproInv>0))
plot(ReproInv~height, SummaryInd, log="xy",col=col.spp[as.factor(species)],pch=16)
legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
words.bottom.right.logxy(mod)

mod <- lm((PropH)~log(ReproInv), data=subset(SummaryInd,ReproInv>0))
plot((ReproInv)~(PropH), SummaryInd, log="y",col=col.spp[as.factor(species)],pch=16,xlim=c(4e-03,1))
legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
```

###Plots of size against RA
* RA not significantly correlated with total height or weight, but of course across and within species effects opposite - bigger individuals of a species have higher RA, but species that are overall bigger have lower RA
* Therefore, there is a negative correlation between PropH (proportion of a species' maximum height) and RA; highly significant, but very low R^2

```{r, echo=FALSE,message=FALSE, fig.width=7, fig.height=7}
par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.1,0.2)) 
mod <- lm(log(FinalWeight)~asin(sqrt(RA)), data=subset(SummaryInd,ReproInv>0))
plot(asin(sqrt(RA))~FinalWeight, SummaryInd, log="x",col=col.spp[as.factor(species)],pch=16)
legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
words.top.right.logx(mod)

mod <- lm(log(height)~asin(sqrt(RA)), data=subset(SummaryInd,ReproInv>0))
plot(asin(sqrt(RA))~height, SummaryInd, log="x",col=col.spp[as.factor(species)],pch=16)
legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
words.top.right.logx(mod)

mod <- lm((PropH)~asin(sqrt(RA)), data=subset(SummaryInd,ReproInv>0))
plot((asin(sqrt(RA)))~(PropH), SummaryInd,col=col.spp[as.factor(species)],pch=16,xlim=c(4e-03,1))
legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
words.bottom.right(mod)
```

##RA schedules (vs. age and height)  
- RA schedules still look "best" plotted against age  
- RA schedules plotted against height are particularly good for a number of species such as EPMI, COER, PELA  
  1. they also show that for PILI that among individuals that reproduce, the "potential" RA decreases with increasing propH  
  2. when all data points are included, all species except PEPU, PHPH, and PULU show increasing RA with increasing height  
  3. when RA =0 is excluded, the following species still have a significant positive correlation: BOLE, COER, EPMI, GRBU, GRSP, HATE. LEES and PELA have a p-value between 0.05-0.10   
  4. PEPU has the lowest slope - matches Mark's suggestion that it is "hanging on"  
- There are species - such as BOLE - which have a much "cleaner" plot against age instead of height (or any other size measure). This indicates that these species are programmed to reproduce at a certain "rate" regardless of their size

```{r, echo=FALSE,message=FALSE, fig.width=14, fig.height=7}
yvar <- "RA"
xvar <- "age"

yvar2 <- "RA"
xvar2 <- "height"

@@

}  
```

* RA vs. height by species  
```{r, echo=FALSE, message=FALSE}
yvar <- "RA"
xvar <- "height"

data <- subset(SummaryInd,RA>0)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(asin(sqrt(x[[yvar]])) ~  log(x[[xvar]])))
results <- summarise_all_fits(lmfits)

* RA vs. age by species  
```{r, echo=FALSE, message=FALSE}
yvar <- "RA"
xvar <- "age"

data <- subset(SummaryInd)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(asin(sqrt(x[[yvar]])) ~  log(x[[xvar]])))
results <- summarise_all_fits(lmfits)

###RV curves, by age, weight and height
```{r, echo=FALSE,message=FALSE, fig.width=21, fig.height=7}
yvar <- "ReproInv"
xvar <- "age"

@@

yvar3 <- "ReproInv"
xvar3 <- "height"

@@

for(spp in names(data)) {
  par(mfrow=c(1,3), cex=1, omi=c(.1,0.3,.5,0.2), mai=c(1.2,1,.5,0.2))  
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar, 
                    main=spp, ,log="xy", xlab=xvar, ylab=yvar)
  plot_yvar2_vs_xvar2(data[[spp]], yvar2, xvar2, 
                      main=spp, log="xy", xlab=xvar2, ylab="")
  plot_yvar3_vs_xvar3(data[[spp]], yvar3, xvar3, 
                      main=spp, log="xy", xlab=xvar3, ylab="")
}  
```

* Reproductive investment vs. height for each species
```{r, echo=FALSE,message=FALSE, fig.width=7, fig.height=7}
yvar <- "ReproInv"
xvar <- "height"

data <- SummaryInd
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(log(x[[yvar]]+1) ~  log(x[[xvar]]+1)))
results <- summarise_all_fits(lmfits)

* Reproductive investment vs. weight for each species
```{r, echo=FALSE,message=FALSE, fig.width=7, fig.height=7}
yvar <- "ReproInv"
xvar <- "FinalWeight"

@@

@@

```{r, echo=FALSE,message=FALSE}
par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.1,0.2)) 
mod <- lm(log(GrowthInv)~log(ReproInv),data=subset(SummaryInd,ReproInv>0))
plot((1+ReproInv)~GrowthInv, SummaryInd, log="xy", col=col.spp[as.factor(species)],pch=16)
legend("bottomright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
words.bottom.right.logxy(mod)
```

@@

```{r, echo=FALSE,message=FALSE}
par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.1,0.2)) 
mod <- lm(RGR~asin(sqrt(RA))*species,data=subset(SummaryInd,RA>0))
plot((RA+.01)~RGR, SummaryInd, log="xy", col=col.spp[as.factor(species)],pch=16)
legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
words.top.right.logxy(mod)
```

@@

###Looking jointly at effects of RA and PropH on growth inveestment
- Model analyzed is: lm(log([[GrowthInv]]) ~  asin(sqrt([[RA]]))*asin(sqrt([[PropH]]))))  
- The canopy species have, not suprisingly, a very obvious maxH, with Growth Investment or RGR tapering markedly at the maxH is approached. In these species growth investment is poorly correlated with RA, but well correlated with height.  
- In some of the mid-height species (GRSP, BOLE, GRBU), growth investment is very poorly correlated with height, but better correlated with RA - in other words, increased RA = less growth.  
- One of the difficult features interpreting this, is that there are species with overall higher correlations and overall lower correlations, and this pattern dominates, not the relative strength  
- My current analyses still lack the ability to tease apart the most obvious pattern - because I don't actually want to show that growth and height are correlated, so much as that the   asymptoting of growth is correlated with height - i.e. the change in slope of the relationship.  
```{r, echo=FALSE, message=FALSE, out.width=900, out.height=576}
yvar <- "GrowthInv"
xvar <- "RA"
x2var <- "PropH"

@@
